### 2022-10-17 sections/conferences-full.tex
Update conferences-full.tex

\begin{benumerate}{74}

\item{González-Bustamante, B., \& Aguilar, D. (2022). {\itshape Digital Development and Open Government: Evidence from Chilean Local Governments}. Presentation delivered at the Digital Democracy Workshop, Digital Society Initiative, University of Zurich, Zurich.}\vspace{1mm}

@@

\item{\small Fleming, T. G., González-Bustamante, B., \& Schleiter, P. (2021). {\itshape Cabinet Reshuffles and Parliamentary No-Confidence Motions}. Presentation delivered at the Otto-Friedrich-Universität Bamberg Workshop, Virtual.}\vspace{1mm}

>>>>

\begin{benumerate}{77}

\item{González-Bustamante, B. (2022, {\itshape forthcoming}). {\itshape Machine Learning and Political Events: Application of Semisupervised Approach to Produce a Data Set on Latin American Cabinets}. Presentation delivered at the II Training Data Lab Workshop, Virtual.}\vspace{1mm}

\item{González-Bustamante, B., \& Aguilar, D. (2022, {\itshape forthcoming}). {\itshape Digital Development and Open Government: Evidence from Chilean Local Governments}. Presentation delivered at the Digital Democracy Workshop, Digital Society Initiative, University of Zurich, Zurich.}\vspace{1mm}

\item{González-Bustamante, B. (2022). {\itshape Machine Learning for the Study of Political Events: Application of Semisupervised Models on Latin American Archives}. Presentation delivered at the LatinR Conference, Virtual.}\vspace{1mm}

\item{González-Bustamante, B., \& Aguilar, D. (2022). {\itshape Integrated Repository on Local Government Indicators in Chile}. Presentation delivered at the LatinR Conference, Virtual.}\vspace{1mm}

@@

\item{\small Fleming, T. G., González-Bustamante, B., \& Schleiter, P. (2021). {\itshape Cabinet Reshuffles and Parliamentary No-Confidence Motions}. Presentation delivered at the Workshop on Coalition Politics and Portfolio Design at the University of Bamberg, Virtual.}\vspace{1mm}
